Shaking out the idiosyncracies

### 2020-02-12 analysis/reports/vetting.Rmd
use 10k not 1k

all_di_macd <- readd(all_di_manip, cache = cache)

>>>>

all_di_macd <- readd(all_di_manip, cache = cache) 
macd_dat <- readd(dat_s_dat_macdb, cache = cache)

DBI::dbDisconnect(db)
rm(cache)

macd_dat <- macd_dat %>%
  group_by(site, dat, singletons, sim, source) %>%
  summarize(s0 = max(rank),
            n0 = sum(abund)) %>%
  ungroup()

all_di_macd <- left_join(all_di_macd, macd_dat, by = c("site", "dat", "singletons", "sim", "source"))

ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()

ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, nsamples >= 2000), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()
